---
title: "TuEtAl_AnalysisReplication"
author: "Nicole Merullo"
date: "2023-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(faux)
```
## Simulate Data of Child Study

There are four subgroups: black males, white males, black females, and white females.

Assume each distribution is normal and use rnorm()


```{r black-males}
set.seed(823)
cmb.age <- rnorm(113, mean = 14.09, sd = 2.62)
cmb.sys <- rnorm(113, mean = 111, sd = 11.637)
cmb.dia <- rnorm(113, mean = 67.31, sd = 10.867)
cmb.bmi <- rnorm(113, mean = 23.91, sd = 6.950)
```

simulate correlation relationship between variables when simulation
simulate correlated variables rnorm_multi() in package faux
I made the systolic/diastolic correlation 0.74 because i found a paper that said that
emipirical = true

The order of the variables is: age, systolic blood pressure, diastolic blood pressure, serum renin, serum aldosterone
choosing not to use BMI because there are no correlations given in the paper
```{r black-males}
black.male.children <- rnorm_multi(n= 62,
                                   mu = c(14.09, 111, 67.31, 3.14, 9.28),
                                   sd = c(2.62, 11.637, 10.867, 2.384, 6.133),
                                   r = c())
```
R = matrix(cbind(1.0, -.-, -.-, ))
Age to age, age to sys, age to dia, age to renin, age to ald

R = matrix(cbind(1, 0.8, -0.5, 0, 0.8, 1, -0.3, 0.3, -0.5, -0.3, 1, 0.6, 0,
    0.3, 0.6, 1), nrow = 4)
    [,1] [,2] [,3] [,4] [,5]
[1,]  1.0  0.8 -0.5  0.0
[2,]  0.8  1.0 -0.3  0.3
[3,] -0.5 -0.3  1.0  0.6
[4,]  0.0  0.3  0.6  1.0
[5,]  